\TheTitle

### 2016-04-19 linvis.tex
Updated Abstract and new tabulation
Re-wrote and re-worked the abstract section.

Changed from hard-tabs to soft-tabs.

\title{\TheTitle}
\author{
\IEEEauthorblockA{\TheAuthors}
\IEEEauthorblockN{Department of Computer Science,
                    University of Victoria, Canada.}
\IEEEauthorblockA{Email: \TheEmails}
}
\maketitle
\begin{abstract}
	With an average of over 900 top-level merges into the Linux kernel per
	release, some containing thousands of commits, many containing hundreds
	of commits, maintenance of older versions of the kernel becomes nearly
	impossible. For security, performance, and changing hardware needs,
	maintainers must understand the changes made to current versions of the
	kernel, and understand how these changes fit into older version in
        order to make the necessary merges and modifications to the older
        versions. Current tools provide information about repositories through
        the directed acyclic graph (DAG) which is helpful for smaller projects,
        but with the scale and number of branches in the kernel, the DAG
        becomes overwhelming very quickly.

	In this paper, we present a tool that uses the dataset collected by
	German et al. to build a tool that uses a tree-based model instead of
        the DAG. This tool is designed to cater to the needs of users looking
        for a top-down approach, or a bottom-up approach to navigating the
        commit information of the kernel.
\end{abstract}

@@

Maintainers of older version of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects
that are the scale of the kernel. Tools like Gitk provide users with the
full view of the DAG, showing all of the merges and commits. For smaller
projects, this information is useful, showing the relation between various
branches. The DAG becomes a tangled mess (\ref{fig:gitk}) of commits, merges,
and the links between them with large modular projects, like the Linux kernel,
making it difficult to derive an explanation of the changes made. In other
cases, the kernel is simply too large for the system to generate a
visualization for. Github provides a DAG view for most projects, but is unable
to display the visualization for projects as large as the Linux kernel.

>>>>

\title{\TheTitle}
\author{
\IEEEauthorblockA{\TheAuthors}
\IEEEauthorblockN{Department of Computer Science,
                    University of Victoria, Canada.}
\IEEEauthorblockA{Email: \TheEmails}
}
\maketitle
\begin{abstract}

        With an average of more than 900 top-level merges into the Linux kernel per
        release, many containing hundreds of commits and some containing thousands,
        maintenance of older versions of the kernel becomes nearly impossible.

        Various commercial products, such as the Android platform, run older
        versions of the kernel. Due to security, performance, and changing hardware
        needs, maintainers must understand how updates made to the current version
        of the kernel fit into older versions in order to make the necessary
        patches.

        Current tools provide information about repositories through the directed
        acyclic graph (DAG), which is helpful for smaller projects. However with the
        scale and number of branches in the kernel the DAG becomes overwhelming very
        quickly.

        In this paper, we present a tool that uses a tree-based model, as described
        by German et al., to construct a clearer summary of the changes made. This
        tool is designed to allow users to explore the topology of the repository
        for a given release of the kernel and view an aggregated summary of the
        changes made.

\end{abstract}

@@

Maintainers of older version of the Linux kernel must sift through thousands of
commits with tools that are unable to filter and effectively visualize projects that
are the scale of the kernel. Tools like Gitk provide users with the full view of the
DAG, showing all of the merges and commits. This information is useful in smaller
projects, showing the relation between various branches. The DAG becomes a tangled
mess (\ref{fig:gitk}) of commits, merges, and the links between them with large
modular projects, like the Linux kernel, making it difficult to derive an
explanation of the changes made. In other cases, the kernel is simply too large for
the system to generate a visualization for. Github provides a DAG view for most
projects, but is unable to display the visualization for projects as large as the
Linux kernel.
